Learning how to act: making good decisions with machine learning

### 2017-10-12 thesis/thesis_map.tex
more talk stuff

\epigraph{In vain the grave, with retrospective Eye,
Would from the apparent what conclude the why,
Infer the Motive from the Deed, and show
That what we chanced, was what we meant, to do.}{Alexander Pope}

>>>>

\epigraph{In vain the sage, with retrospective Eye,
Would from the apparent what conclude the why,
Infer the Motive from the Deed, and show
That what we chanced, was what we meant, to do.}{Alexander Pope}
